On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-08 manuscripts/IEEE/final_submission.tex
added noisy learning figure

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=.24 \linewidth]{figs/basis.png}
% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
\caption{\textbf{Noisy dictionary learning}. Recovery of the $8 \times 8$ discrete cosine transform (DCT) basis (the 64 columns of first matrix above) from $8$-sparse samples with linearly increasing noise (using the FastICA algorithm \cite{hyvarinen2000independent}).}
\label{projdata}
\end{center}
\end{figure}
